Predicting Political Support in the United States

### 2024-03-17 output/paper.qmd

# Discussion

what is done and what we learned:::

@@

weaknesses of the analysis::: TODO also talk about small demographic sizes

Although there seems to be a strong correlation between if a voter identifies as an other gender to supporting Biden, and a strong correlation between if a voter identifies as an other race to supporting Biden, but these must be considered carefully as within the sample (with seed 302), only 5 and 1 voters identified in those categories respectively. To get a more accurate reading in regards to these features, it would be necessary to train a model which includes much more of these demographics.

future steps to learn in the future:::

TODO talk about the change or no change that occurs in the 2024 election, and if respondents of different demographics had changed their minds after Biden's term. If people who had their student loans forgiven will still vote for Biden, or vote for Trump after their needs from Biden have already been met.

>>>>

# Discussion {#discussion}

@@

Although there seems to be a strong correlation between if a voter identifies as an other gender to supporting Biden, and a strong correlation between if a voter identifies as an other race to supporting Biden, but these must be considered carefully as within the sample (with seed 302), only 5 and 1 voters identified in those categories respectively. There were various other demographics in the dataset that had relatively small sample sizes, such as: `race` where non black, white, or hispanic respondents made up a small portion of the sample, or non Catholic, Protestant, or Atheist respondents in `religion`. To get a more accurate reading in regards to these features, it would be necessary to train a model which includes a larger sample size of these demographics or to find a way to account for these values while still making use of them. This was a scenario that one may expect to see as there can always be underrepresented demographics in a 60000 respondent sized sample. This is a big limitation to our models, and is something that should be considered when interpreting the results.

For future steps, we hope to be able to observe any changes that arise in the upcoming 2024 election. Since the results we have interpreted from the 2022 CES dataset are based on voter's stances at the time, there could be a possibility that the voter's stances have changed nearing the end of Biden's term. It would also be good to see if the results from the our models are consistent with the results from the upcoming 2024 election. Should there be any consistency, would it raise the question of whether the voter's stances are more influenced by their cultural background and personal stances, or if their support is more influenced by the continuously changing platform that each party stands on. There are some areas that would be interesting to observe if Harvard were to conduct a 2024 CES survey, such as if previous Biden voters would still vote for him considering how he has handled the student loan forgiveness situation. Would a voter who has their student loans forgiven this term still vote for Biden since their needs have already been met? It would also be note worthy to take a look at how stances have changed on household gun ownership and if it has affected their support in the presidential election. As more shootings in the country are recorded, will the number of gun owners increase? Will this affect which party they support, considering the different stances on gun ownership laws? These are all questions that we hope could be answered after the outcome of the 2024 election.
